### 2023-03-29 response-to-audit-report.md

# DRAFT Response to Audit Report

TODO:

- [ ] Add prefatory text and executive summary.
- [ ] Add responses and mitigation commits to Isabelle-related findings.
- [x] Add responses and mitigation commits to Haskell-related findings.
- [ ] Fix display of equations or replace ones that cannot be fixed with ellipses ("...").
- [ ] Replace broken links and cross references, or use elipses ("...").
- [ ] Verify the section numbering is correct.
- [ ] Add table of contents.
- [ ] Proofread.

## Executive Summary

TODO: @bwbush will add text here after everything else is written.

## Acknowledgement

TODO: @bwbush will add text thanking the audit team.

## Overview of Isabelle Changes

## Overview of Changes to Marlowe-Cardano Specification and Haskell (Plutus) Implementation

The audit report's main and high-severity concerns for the Plutus validators for Marlowe on Cardano fell into to four clusters:

1. Incorrect handling of negative deposits
    - "2.1.1 Negative deposits allow stealing funds"
2. Incomplete prevention of double satisfaction
    - "2.1.2 Contracts vulnerable to double satisfaction attacks"
3. Lax enforcement of invariants in Marlowe state
    - "2.1.7 Positive balances are not checked for the output state"
    - "2.1.8 Non-validated Marlowe states"
    - "2.1.9 Total balance of ending state uncomputed"
    - "2.1.10 Unchecked ending balance"
4. Difference semantics of association lists in Isabelle and Plutus
    - "2.1.12 Different insertion functions used in Isabelle and Haskell code"

Incorrect handling of negative deposits (item 1 above) was mitigated by the addition of a guard against this in Marlowe's Plutus validator so that its behavior was consistent with Marlowe semantics. Property-based tests were also added to check the correctness of the mitigation.

Although the Marlowe validator had prevented double-satisfaction among multiple copies of the Marlowe validator script running in the same transaction, it did not prevent double-satisfaction in cases where the Marlowe validator run alongside another Plutus validator in the same transaction (item 2 above). Double satisfaction has now been prevented by enforcing that the Marlowe validator is the only Plutus script that runs in transactions that make payments to parties. This allows Marlowe contracts to coordinate with other Plutus scripts, but only under conditions where double satisfaction is impossible. Once again, property-based tests were added to check the correctness of this mitigation.

The Marlowe validator had made optimistic assumptions about its own correct operation and hence did not check certain invariants in order to save on Plutus execution costs (item 3 above). The Marlowe semantics validator has now been thoroughly hardened against corruption of initial or final state so that it ensures that the three state-invariants of positive accounts, non-duplication of state entries (accounts, choices, and bound values), and a total internal value matching the script UTxO's value. This hardening was completed without unduly increasing the size (in bytes) of the validator or its Plutus execution cost: such was verified with simulated and on-chain measurement of execution costs for a library of real-life Marlowe contracts. Notably, the enforcement of the final invariants protects against funds becoming permanently locked in a Marlowe contract due to a garbled state: even in cases where the implementation of Marlowe semantics or parts of the Plutus validator are flawed, at least some of the execution paths of a Marlowe contract remain viable, so funds could be released even under nominally impossible but catastrophic difficulties. The property-based test suite was significantly enhanced to

Mitigation of the difference between association lists (item 4 above) in Isabelle (`MList`) and Plutus (`AssocMap`) was handled by the aforementioned enforcement of invariants, by line-by-line code inspection and annotation, and by thoroughly enhanced property-based testing. Work is in progress on a formal proof of the equivalence of `MList` and `AssocMap` under pre-conditions that hold within Marlowe semantics. Note that porting Isabelle's `MList` implementation to Plutus would have enlarged the Marlowe semantics validator by at least 2000 bytes and rendered it too costly to execute within the Cardano ledger's present execution-cost limits.

The audit report for Marlowe on Cardano was based on the commit hash [523f3d56](https://github.com/input-output-hk/marlowe-cardano/commit/523f3d56f22bf992ddb0b0c8a52bb7a5a188f9e9). The revisions and mitigations discussed here apply to [69468d66](https://github.com/input-output-hk/marlowe-cardano/commit/69468d6623e24a4ccd6659e378ae012c38ca01ce) of that repository. The appendix to this report list the differences between pre- and post-audit validator code for Marlowe on Cardano.

The medium-severity concerns in the audit report center around missing tests or name shadowing. With the exception of "2.7.1 More precise failure checks", these have all been remedied either by code changes (in the case of the shadowing) or by the addition of a significant augmentation of the property-based test suite. The audit's low-severity concerns generally relate to insufficiently detailed text in the Marlowe Cardano specification, the need for more elaborate comments in the code, naming of variable bindings, or typographical errors. Nearly all of these finds have been addressed, with only the exception of a few cosmetic recommendations that were not adopted.

# 2 Responses to Specific Findings

@@

> **File `Spec/Marlowe/Plutus/Specification.hs`, `Various tests`** 
> 
> The tests use the functions `checkSemanticsTransaction` and `checkPayoutTransaction` to verify that various error conditions cause transactions to be rejected. These functions test that a transaction passes or fails, but when it fails, the functions do not consider the error cause. Checking the exact cause is necessary to ensure the transaction is rejected because of the intended reason and not because of some other error condition arising in a particular test case by coincidence.
> 
> The absence of this information makes it easier to accidentally produce a test that is not testing what is intended.

TODO: @bwbush will add text here.

### 2.7.2 Missing tests *(Severity: Medium)*

> **File `Spec/Marlowe/Semantics/Compute.hs`, ``** 
> 
> The following properties could additionally be tested for `computeTransaction`:
> -   payment subtracts from an account,
> -   deposit adds to an account,
> -   `INotify` input produces the expected continuation,
> -   `IChoice` input produces the expected continuation,
> -   the hash of a successfully applied merkleized input matches the hash of the merkleized case.
> 
> Some of these are tested in `Spec/Marlowe/Semantics/Functions.hs` already for auxiliary functions.

Commit [ee2e5222](https://github.com/input-output-hk/marlowe-cardano/commit/ee2e52220e25736af29a1f01144d5fafbe9eed76) adds a property-based test that choice and deposit continue as expected; commit [333eee29](https://github.com/input-output-hk/marlowe-cardano/commit/333eee293aa3afe95d0aa7f678c7e7b7bad660ea) tests that choice produces expected continuation; commit [477284c7](https://github.com/input-output-hk/marlowe-cardano/commit/477284c78095482eba63adc2e6090ea68553db9d) tests that that deposits add to an account; commit [d241669b](https://github.com/input-output-hk/marlowe-cardano/commit/d241669bfb7ec8dad1cc92a7ca6185d08229817e) tests that payout substracts from an account; and commit [f33fc720](https://github.com/input-output-hk/marlowe-cardano/commit/f33fc7206522031c93253323f3b8ca083d8ca8c7) tests that Merkleization continues as expected.

> **File `Spec/Marlowe/Semantics/Functions.hs`, `Missing merkleization tests`** 
> 
> The properties in this module do not seem to be tested with merkleized contracts or inputs except for `checkGetContinuation`. More merkleization tests should be added.

Commits [2a936bf1](https://github.com/input-output-hk/marlowe-cardano/commit/2a936bf1bbb890cc811b966b46a10fd38314dc25) and [8f8183d7](https://github.com/input-output-hk/marlowe-cardano/commit/8f8183d7f14c6bdc3841a1999077ef01ebac4144) significantly increase the coverage of merkleization in validator tests by utilizing a much larger set of test contracts and adding a probability that almost any test will involve a merkleized contract.

> **File `Spec/Marlowe/Semantics/Compute.hs`, function `checkFixInterval`, lines *100-102***
> 
> The test `checkFixInterval` is never instantiated with an invalid interval that is in the past, meaning the function `fixInterval` is never tested for that case.

Commit [811f048b](https://github.com/input-output-hk/marlowe-cardano/commit/811f048ba93db10972641c0c235864db1d6014e7) adds a property-based test for an invalid in terval in the past.

## Appendix: Post-Audit Changes in Marlowe Validator

```bash
git diff 523f3d56f22bf992ddb0b0c8a52bb7a5a188f9e9 69468d6623e24a4ccd6659e378ae012c38ca01ce marlowe/src/Language/Marlowe/{Core/V1/Semantics*,Scripts.hs}
```

```diff
diff --git a/marlowe/src/Language/Marlowe/Core/V1/Semantics.hs b/marlowe/src/Language/Marlowe/Core/V1/Semantics.hs
index e31b8c478..82b57b903 100644
--- a/marlowe/src/Language/Marlowe/Core/V1/Semantics.hs
+++ b/marlowe/src/Language/Marlowe/Core/V1/Semantics.hs
@@ -94,12 +94,12 @@ module Language.Marlowe.Core.V1.Semantics
   , TransactionError(..)
   , TransactionWarning(..)
     -- * Utility Functions
+  , allBalancesArePositive
   , contractLifespanUpperBound
   , isClose
   , notClose
   , paymentMoney
   , totalBalance
-  , validateBalances
     -- * Serialisation
   , currencySymbolFromJSON
   , currencySymbolToJSON
@@ -217,6 +217,26 @@ import Text.PrettyPrint.Leijen (comma, hang, lbrace, line, rbrace, space, text,
 data Payment = Payment AccountId Payee Token Integer
   deriving stock (Haskell.Eq, Haskell.Show)

+instance ToJSON Payment where
+  toJSON (Payment accountId payee token amount) =
+    object
+      [
+        "payment_from" .= accountId
+      , "to" .= payee
+      , "token" .= token
+      , "amount" .= amount
+      ]
+
+instance FromJSON Payment where
+  parseJSON =
+    withObject "Payment"
+      $ \o ->
+        Payment
+          <$> o .: "payment_from"
+          <*> o .: "to"
+          <*> o .: "token"
+          <*> o .: "amount"
+

 -- | Extract the money value from a payment.
 paymentMoney :: Payment -> Money
@@ -293,7 +313,28 @@ data TransactionError = TEAmbiguousTimeIntervalError
                       | TEUselessTransaction
                       | TEHashMismatch
   deriving stock (Haskell.Show, Generic, Haskell.Eq)
-  deriving anyclass (ToJSON, FromJSON)
+
+instance ToJSON TransactionError where
+  toJSON TEAmbiguousTimeIntervalError = JSON.String "TEAmbiguousTimeIntervalError"
+  toJSON TEApplyNoMatchError = JSON.String "TEApplyNoMatchError"
+  toJSON (TEIntervalError intervalError) = object ["error" .= JSON.String "TEIntervalError", "context" .= intervalError]
+  toJSON TEUselessTransaction = JSON.String "TEUselessTransaction"
+  toJSON TEHashMismatch = JSON.String "TEHashMismatch"
+
+instance FromJSON TransactionError where
+  parseJSON (JSON.String s) =
+    case s of
+      "TEAmbiguousTimeIntervalError" -> return TEAmbiguousTimeIntervalError
+      "TEApplyNoMatchError" -> return TEApplyNoMatchError
+      "TEUselessTransaction" -> return TEUselessTransaction
+      "TEHashMismatch" -> return TEHashMismatch
+      _ -> Haskell.fail "Failed parsing TransactionError"
+  parseJSON (JSON.Object o) = do
+                                err <- o .: "error"
+                                if err Haskell.== ("TEIntervalError" :: Haskell.String)
+                                  then TEIntervalError <$> o .: "context"
+                                  else Haskell.fail "Failed parsing TransactionError"
+  parseJSON _ = Haskell.fail "Failed parsing TransactionError"

 -- | Marlowe transaction input.
@@ -319,6 +360,31 @@ data TransactionOutput =
     | Error TransactionError
   deriving stock (Haskell.Show)

+instance ToJSON TransactionOutput where
+  toJSON TransactionOutput{..} =
+    object
+      [
+        "warnings" .= txOutWarnings
+      , "payments" .= txOutPayments
+      , "state" .= txOutState
+      , "contract" .= txOutContract
+      ]
+  toJSON (Error err) = object ["transaction_error" .= err]
+
+instance FromJSON TransactionOutput where
+  parseJSON =
+    withObject "TransactionOutput"
+      $ \o ->
+        let
+          asTransactionOutput =
+            TransactionOutput
+              <$> o .: "warnings"
+              <*> o .: "payments"
+              <*> o .: "state"
+              <*> o .: "contract"
+          asError = Error <$> o .: "transaction_error"
+        in
+          asTransactionOutput <|> asError

 -- | Parse a validator hash from JSON.
 validatorHashFromJSON :: JSON.Value -> Parser ValidatorHash
@@ -404,12 +470,22 @@ evalValue env state value = let
                                    then 0
                                    else n `Builtins.quotientInteger` d
         ChoiceValue choiceId ->
+            -- SCP-5126: Given the precondition that `choices` contains no
+            -- duplicate entries, this lookup behaves identically to
+            -- Marlowe's Isabelle semantics given the precondition that
+            -- the initial state's `choices` in Isabelle was sorted and
+            -- did not contain duplicate entries.
             case Map.lookup choiceId (choices state) of
                 Just x  -> x
                 Nothing -> 0
         TimeIntervalStart    -> getPOSIXTime (fst (timeInterval env))
         TimeIntervalEnd      -> getPOSIXTime (snd (timeInterval env))
         UseValue valId       ->
+            -- SCP-5126: Given the precondition that `boundValues` contains
+            -- no duplicate entries, this lookup behaves identically to
+            -- Marlowe's Isabelle semantics given the precondition that
+            -- the initial state's `boundValues` in Isabelle was sorted
+            -- and did not contain duplicate entries.
             case Map.lookup valId (boundValues state) of
                 Just x  -> x
                 Nothing -> 0
@@ -425,6 +501,11 @@ evalObservation env state obs = let
         AndObs lhs rhs          -> evalObs lhs && evalObs rhs
         OrObs lhs rhs           -> evalObs lhs || evalObs rhs
         NotObs subObs           -> not (evalObs subObs)
+                                   -- SCP-5126: Given the precondition that `choices` contains no
+                                   -- duplicate entries, this membership test behaves identically
+                                   -- to Marlowe's Isabelle semantics given the precondition that
+                                   -- the initial state's `choices` in Isabelle was sorted and did
+                                   -- not contain duplicate entries.
         ChoseSomething choiceId -> choiceId `Map.member` choices state
         ValueGE lhs rhs         -> evalVal lhs >= evalVal rhs
         ValueGT lhs rhs         -> evalVal lhs > evalVal rhs
@@ -439,6 +520,12 @@ evalObservation env state obs = let
 refundOne :: Accounts -> Maybe ((Party, Token, Integer), Accounts)
 refundOne accounts = case Map.toList accounts of
     [] -> Nothing
+    -- SCP-5126: The return value of this function differs from
+    -- Isabelle semantics in that it returns the least-recently
+    -- added account-token combination rather than the first
+    -- lexicographically ordered one. Also, the sequence
+    -- `Map.fromList . tail . Map.toList` preserves the
+    -- invariants of order and non-duplication.
     ((accId, token), balance) : rest ->
         if balance > 0
         then Just ((accId, token, balance), Map.fromList rest)
@@ -447,18 +534,30 @@ refundOne accounts = case Map.toList accounts of

 -- | Obtains the amount of money available an account.
 moneyInAccount :: AccountId -> Token -> Accounts -> Integer
-moneyInAccount accId token accounts = case Map.lookup (accId, token) accounts of
-    Just x  -> x
-    Nothing -> 0
+moneyInAccount accId token accounts =
+    -- SCP-5126: Given the precondition that `accounts` contains
+    -- no duplicate entries, this lookup behaves identically to
+    -- Marlowe's Isabelle semantics given the precondition that
+    -- the initial state's `accounts` in Isabelle was sorted and
+    -- did not contain duplicate entries.
+    case Map.lookup (accId, token) accounts of
+      Just x  -> x
+      Nothing -> 0

 -- | Sets the amount of money available in an account.
 updateMoneyInAccount :: AccountId -> Token -> Integer -> Accounts -> Accounts
 updateMoneyInAccount accId token amount =
+    -- SCP-5126: Given the precondition that `accounts` contains
+    -- no duplicate entries, this deletion or insertion behaves
+    -- identically (aside from internal ordering) to Marlowe's
+    -- Isabelle semantics given the precondition that the initial
+    -- state's `accounts` in Isabelle was sorted and did not
+    -- contain duplicate entries.
     if amount <= 0 then Map.delete (accId, token) else Map.insert (accId, token) amount

--- | Add the given amount of money to an accoun (only if it is positive).
+-- | Add the given amount of money to an account (only if it is positive).
 --   Return the updated Map.
 addMoneyToAccount :: AccountId -> Token -> Integer -> Accounts -> Accounts
 addMoneyToAccount accId token amount accounts = let
@@ -482,6 +581,14 @@ giveMoney accountId payee token amount accounts = let
 reduceContractStep :: Environment -> State -> Contract -> ReduceStepResult
 reduceContractStep env state contract = case contract of

### 2023-03-29 response-to-audit-report.md

+    -- SCP-5126: Although `refundOne` refunds accounts-token combinations
+    -- in least-recently-added order and Isabelle semantics requires that
+    -- they be refunded in lexicographic order, `reduceContractUntilQuiescent`
+    -- ensures that the `Close` pattern will be executed until `accounts`
+    -- is empty. Thus, the net difference between the behavior here and the
+    -- Isabelle semantics is that the `ContractQuiescent` resulting from
+    -- `reduceContractUntilQuiescent` will contain payments in a different
+    -- order.
     Close -> case refundOne (accounts state) of
         Just ((party, token, amount), newAccounts) -> let
             newState = state { accounts = newAccounts }
@@ -522,7 +629,17 @@ reduceContractStep env state contract = case contract of
     Let valId val cont -> let
         evaluatedValue = evalValue env state val
         boundVals = boundValues state
+        -- SCP-5126: Given the precondition that `boundValues` contains
+        -- no duplicate entries, this insertion behaves identically
+        -- (aside from internal ordering) to Marlowe's Isabelle semantics
+        -- given the precondition that the initial state's `boundValues`
+        -- in Isabelle was sorted and did not contain duplicate entries.
         newState = state { boundValues = Map.insert valId evaluatedValue boundVals }
+        -- SCP-5126: Given the precondition that `boundValues` contains
+        -- no duplicate entries, this lookup behaves identically to
+        -- Marlowe's Isabelle semantics given the precondition that the
+        -- initial state's `boundValues` in Isabelle was sorted and did
+        -- not contain duplicate entries.
         warn = case Map.lookup valId boundVals of
               Just oldVal -> ReduceShadowing valId oldVal evaluatedValue
               Nothing     -> ReduceNoWarning
@@ -575,6 +692,11 @@ applyAction env state (IDeposit accId1 party1 tok1 amount) (Deposit accId2 party
     else NotAppliedAction
 applyAction _ state (IChoice choId1 choice) (Choice choId2 bounds) =
     if choId1 == choId2 && inBounds choice bounds
+    -- SCP-5126: Given the precondition that `choices` contains no
+    -- duplicate entries, this insertion behaves identically (aside
+    -- from internal ordering) to Marlowe's Isabelle semantics
+    -- given the precondition that the initial state's `choices`
+    -- in Isabelle was sorted and did not contain duplicate entries.
     then let newState = state { choices = Map.insert choId1 choice (choices state) }
          in AppliedAction ApplyNoWarning newState
     else NotAppliedAction
@@ -592,18 +714,20 @@ getContinuation (MerkleizedInput _ inputContinuationHash continuation) (Merkleiz
     else Nothing
 getContinuation _ _ = Nothing

--- | Try to apply an input to a list of cases.
+-- | Try to apply an input to a list of cases, accepting the first match.
 applyCases :: Environment -> State -> Input -> [Case Contract] -> ApplyResult
-applyCases env state input (headCase : tailCase) =
+applyCases env state input (headCase : tailCases) =
     let inputContent = getInputContent input :: InputContent
         action = getAction headCase :: Action
         maybeContinuation = getContinuation input headCase :: Maybe Contract
     in case applyAction env state inputContent action of
          AppliedAction warning newState ->
+           -- Note that this differs from Isabelle semantics because
+           -- the Cardano semantics includes merkleization.
            case maybeContinuation of
              Just continuation -> Applied warning newState continuation
              Nothing           -> ApplyHashMismatch
-         NotAppliedAction -> applyCases env state input tailCase
+         NotAppliedAction -> applyCases env state input tailCases
 applyCases _ _ _ [] = ApplyNoMatchError

@@ -615,7 +739,7 @@ applyInput _ _ _ _                          = ApplyNoMatchError

 -- | Propagate 'ReduceWarning' to 'TransactionWarning'.
 convertReduceWarnings :: [ReduceWarning] -> [TransactionWarning]
-convertReduceWarnings = foldr (\warn acc -> case warn of
+convertReduceWarnings = foldr (\warn acc -> case warn of  -- Note that `foldr` is used here for efficiency, differing from Isabelle.
     ReduceNoWarning -> acc
     ReduceNonPositivePay accId payee tok amount ->
         TransactionNonPositivePay accId payee tok amount : acc
@@ -655,12 +779,12 @@ applyAllInputs env state contract inputs = let
                     curState
                     cont
                 (input : rest) -> case applyInput env curState input cont of
-                    Applied applyWarn newState cont ->
+                    Applied applyWarn newState cont' ->
                         applyAllLoop
                             True
                             env
                             newState
-                            cont
+                            cont'
                             rest
                             (warnings' ++ convertApplyWarning applyWarn)
                             payments'
@@ -759,8 +883,8 @@ totalBalance accounts = foldMap

 -- | Check that all accounts have positive balance.
-validateBalances :: State -> Bool
-validateBalances State{..} = all (\(_, balance) -> balance > 0) (Map.toList accounts)
+allBalancesArePositive :: State -> Bool
+allBalancesArePositive State{..} = all (\(_, balance) -> balance > 0) (Map.toList accounts)

 instance FromJSON TransactionInput where
@@ -845,20 +969,26 @@ instance Eq Payment where
 instance Eq ReduceWarning where
     {-# INLINABLE (==) #-}
     ReduceNoWarning == ReduceNoWarning = True
-    (ReduceNonPositivePay acc1 p1 tn1 a1) == (ReduceNonPositivePay acc2 p2 tn2 a2) =
+    ReduceNoWarning == _ = False
+    ReduceNonPositivePay acc1 p1 tn1 a1 == ReduceNonPositivePay acc2 p2 tn2 a2 =
         acc1 == acc2 && p1 == p2 && tn1 == tn2 && a1 == a2
-    (ReducePartialPay acc1 p1 tn1 a1 e1) == (ReducePartialPay acc2 p2 tn2 a2 e2) =
+    ReduceNonPositivePay{} == _ = False
+    ReducePartialPay acc1 p1 tn1 a1 e1 == ReducePartialPay acc2 p2 tn2 a2 e2 =
         acc1 == acc2 && p1 == p2 && tn1 == tn2 && a1 == a2 && e1 == e2
-    (ReduceShadowing v1 old1 new1) == (ReduceShadowing v2 old2 new2) =
+    ReducePartialPay{} == _ = False
+    ReduceShadowing v1 old1 new1 == ReduceShadowing v2 old2 new2 =
         v1 == v2 && old1 == old2 && new1 == new2
-    _ == _ = False
+    ReduceShadowing{} == _ = False
+    ReduceAssertionFailed == ReduceAssertionFailed = True
+    ReduceAssertionFailed == _ = False

 instance Eq ReduceEffect where
     {-# INLINABLE (==) #-}
     ReduceNoPayment == ReduceNoPayment           = True
+    ReduceNoPayment == _                         = False
     ReduceWithPayment p1 == ReduceWithPayment p2 = p1 == p2
-    _ == _                                       = False
+    ReduceWithPayment _ == _                     = False

 -- Lifting data types to Plutus Core
diff --git a/marlowe/src/Language/Marlowe/Core/V1/Semantics/Types.hs b/marlowe/src/Language/Marlowe/Core/V1/Semantics/Types.hs
index a333b8fbb..bf495773b 100644
--- a/marlowe/src/Language/Marlowe/Core/V1/Semantics/Types.hs
+++ b/marlowe/src/Language/Marlowe/Core/V1/Semantics/Types.hs
@@ -108,7 +108,7 @@ import PlutusTx.Lift (makeLift)
 import PlutusTx.Prelude hiding (encodeUtf8, mapM, (<$>), (<*>), (<>))
 import Prelude (mapM, (<$>))
 import qualified Prelude as Haskell
-import Text.PrettyPrint.Leijen (text)
+import Text.PrettyPrint.Leijen (parens, text)

 -- Functions that used in Plutus Core must be inlinable,
@@ -126,8 +126,8 @@ data Party =
   deriving stock (Generic,Haskell.Eq,Haskell.Ord)

 instance Pretty Party where
-  prettyFragment (Address network address) = text $ "Address " ++ Haskell.show (serialiseAddressBech32 network address)
-  prettyFragment (Role role)               = text $ "Role "    ++ Haskell.show role
+  prettyFragment (Address network address) = parens $ text "Address " Haskell.<> prettyFragment (serialiseAddressBech32 network address)
+  prettyFragment (Role role)               = parens $ text "Role "    Haskell.<> prettyFragment role

 instance Haskell.Show Party where
   showsPrec _ (Address network address) = Haskell.showsPrec 11 $ Haskell.show (serialiseAddressBech32 network address)
@@ -307,6 +307,13 @@ data State = State { accounts    :: Accounts
 newtype Environment = Environment { timeInterval :: TimeInterval }
   deriving stock (Haskell.Show,Haskell.Eq,Haskell.Ord)

+instance FromJSON Environment where
+  parseJSON = withObject "Environment"
+    (\v -> Environment <$> (posixIntervalFromJSON =<< v .: "timeInterval"))
+
+instance ToJSON Environment where
+  toJSON Environment{..} = object
+    [ "timeInterval" .= posixIntervalToJSON timeInterval]

 -- | Input for a Marlowe contract. Correspond to expected 'Action's.
 data InputContent = IDeposit AccountId Party Token Integer
@@ -389,23 +396,24 @@ data IntervalError = InvalidInterval TimeInterval
                    | IntervalInPastError POSIXTime TimeInterval
   deriving stock (Haskell.Show, Generic, Haskell.Eq)

+
 instance ToJSON IntervalError where
   toJSON (InvalidInterval (s, e)) = A.object
-    [ ("invalidInterval", toJSON (posixTimeToJSON s, posixTimeToJSON e)) ]
+    [ ("invalidInterval", A.object [("from", posixTimeToJSON s), ("to", posixTimeToJSON e)]) ]
   toJSON (IntervalInPastError t (s, e)) = A.object
-    [ ("intervalInPastError", toJSON (posixTimeToJSON t, posixTimeToJSON s, posixTimeToJSON e)) ]
+    [ ("intervalInPastError", A.object [("minTime", posixTimeToJSON t), ("from", posixTimeToJSON s), ("to", posixTimeToJSON e)]) ]

 instance FromJSON IntervalError where
   parseJSON (JSON.Object v) =
     let
       parseInvalidInterval = do
-        (s, e) <- v .: "invalidInterval"
-        InvalidInterval <$> ((,) <$> posixTimeFromJSON s <*> posixTimeFromJSON e)
+        o <- v .: "invalidInterval"
+        InvalidInterval <$> posixIntervalFromJSON o
       parseIntervalInPastError = do
-        (t, s, e) <- v .: "intervalInPastError"
+        o <- v .: "intervalInPastError"
         IntervalInPastError
-          <$> posixTimeFromJSON t
-          <*> ((,) <$> posixTimeFromJSON s <*> posixTimeFromJSON e)
+          <$> (posixTimeFromJSON =<< o .: "minTime")
+          <*> posixIntervalFromJSON o
     in
       parseIntervalInPastError <|> parseInvalidInterval
   parseJSON invalid =
@@ -422,11 +430,18 @@ posixTimeFromJSON = \case
   invalid ->
       JSON.prependFailure "parsing POSIXTime failed, " (JSON.typeMismatch "Number" invalid)

+posixIntervalFromJSON :: A.Object -> Parser TimeInterval
+posixIntervalFromJSON o = (,) <$> (posixTimeFromJSON =<< o .: "from") <*> (posixTimeFromJSON =<< o .: "to")

 -- | Serialise time as a JSON value.
 posixTimeToJSON :: POSIXTime -> JSON.Value
 posixTimeToJSON (POSIXTime n) = JSON.Number $ scientific n 0

+posixIntervalToJSON :: TimeInterval -> JSON.Value
+posixIntervalToJSON (from, to) = object
+  [ "from" .= posixTimeToJSON from
+  , "to" .= posixTimeToJSON to
+  ]

 -- | Result of 'fixInterval'
 data IntervalResult = IntervalTrimmed Environment State
@@ -778,23 +793,24 @@ instance ToJSON Contract where
 instance Eq Party where
     {-# INLINABLE (==) #-}
     Address n1 a1 == Address n2 a2 = n1 == n2 && a1 == a2
+    Address _ _   == _             = False
     Role r1       == Role r2       = r1 == r2
-    _             == _             = False
+    Role _        == _             = False

 instance Eq ChoiceId where
     {-# INLINABLE (==) #-}
-    (ChoiceId n1 p1) == (ChoiceId n2 p2) = n1 == n2 && p1 == p2
+    ChoiceId n1 p1 == ChoiceId n2 p2 = n1 == n2 && p1 == p2

 instance Eq Token where
     {-# INLINABLE (==) #-}
-    (Token n1 p1) == (Token n2 p2) = n1 == n2 && p1 == p2
+    Token n1 p1 == Token n2 p2 = n1 == n2 && p1 == p2

 instance Eq ValueId where
     {-# INLINABLE (==) #-}
-    (ValueId n1) == (ValueId n2) = n1 == n2
+    ValueId n1 == ValueId n2 = n1 == n2

 instance Pretty ValueId where
@@ -804,78 +820,107 @@ instance Pretty ValueId where
 instance Eq Payee where
     {-# INLINABLE (==) #-}
     Account acc1 == Account acc2 = acc1 == acc2
+    Account{}    == _            = False
     Party p1 == Party p2         = p1 == p2
-    _ == _                       = False
+    Party{}  == _                = False

 instance Eq a => Eq (Value a) where
     {-# INLINABLE (==) #-}
-    AvailableMoney acc1 tok1 == AvailableMoney acc2 tok2 =
-        acc1 == acc2 && tok1 == tok2
+    AvailableMoney acc1 tok1 == AvailableMoney acc2 tok2 = acc1 == acc2 && tok1 == tok2
+    AvailableMoney _    _    == _                        = False
     Constant i1 == Constant i2 = i1 == i2
+    Constant{}  == _           = False
     NegValue val1 == NegValue val2 = val1 == val2
+    NegValue{}    == _             = False
     AddValue val1 val2 == AddValue val3 val4 = val1 == val3 && val2 == val4
+    AddValue{}         == _                  = False
     SubValue val1 val2 == SubValue val3 val4 = val1 == val3 && val2 == val4
+    SubValue{}         == _                  = False
     MulValue val1 val2 == MulValue val3 val4 = val1 == val3 && val2 == val4
+    MulValue{}         == _                  = False
     DivValue val1 val2 == DivValue val3 val4 = val1 == val3 && val2 == val4
+    DivValue{}         == _                  = False
     ChoiceValue cid1 == ChoiceValue cid2 = cid1 == cid2
+    ChoiceValue{}    == _                = False
     TimeIntervalStart == TimeIntervalStart = True
-    TimeIntervalEnd   == TimeIntervalEnd   = True
+    TimeIntervalStart == _                 = False
+    TimeIntervalEnd == TimeIntervalEnd = True
+    TimeIntervalEnd == _               = False
     UseValue val1 == UseValue val2 = val1 == val2
-    Cond obs1 thn1 els1 == Cond obs2 thn2 els2 =  obs1 == obs2 && thn1 == thn2 && els1 == els2
-    _ == _ = False
+    UseValue{}    == _             = False
+    Cond obs1 thn1 els1 == Cond obs2 thn2 els2 = obs1 == obs2 && thn1 == thn2 && els1 == els2
+    Cond{}              == _                   = False

 instance Eq Observation where
     {-# INLINABLE (==) #-}
     AndObs o1l o2l == AndObs o1r o2r           = o1l == o1r && o2l == o2r
+    AndObs{}       == _                        = False
     OrObs  o1l o2l == OrObs  o1r o2r           = o1l == o1r && o2l == o2r
+    OrObs{}        == _                        = False
     NotObs ol == NotObs or                     = ol == or
+    NotObs{}  == _                             = False
     ChoseSomething cid1 == ChoseSomething cid2 = cid1 == cid2
+    ChoseSomething _    == _                   = False
     ValueGE v1l v2l == ValueGE v1r v2r         = v1l == v1r && v2l == v2r
+    ValueGE{}       == _                       = False
     ValueGT v1l v2l == ValueGT v1r v2r         = v1l == v1r && v2l == v2r
+    ValueGT{}       == _                       = False
     ValueLT v1l v2l == ValueLT v1r v2r         = v1l == v1r && v2l == v2r
+    ValueLT{}       == _                       = False
     ValueLE v1l v2l == ValueLE v1r v2r         = v1l == v1r && v2l == v2r
+    ValueLE{}       == _                       = False
     ValueEQ v1l v2l == ValueEQ v1r v2r         = v1l == v1r && v2l == v2r
+    ValueEQ{}       == _                       = False
     TrueObs  == TrueObs                        = True
+    TrueObs  == _                              = False
     FalseObs == FalseObs                       = True
-    _ == _                                     = False
+    FalseObs == _                              = False

 instance Eq Action where
     {-# INLINABLE (==) #-}
     Deposit acc1 party1 tok1 val1 == Deposit acc2 party2 tok2 val2 =
         acc1 == acc2 && party1 == party2 && tok1 == tok2 && val1 == val2
+    Deposit{}       == _ = False
     Choice cid1 bounds1 == Choice cid2 bounds2 =
         cid1 == cid2 && length bounds1 == length bounds2 && let
             bounds = zip bounds1 bounds2
             checkBound (Bound low1 high1, Bound low2 high2) = low1 == low2 && high1 == high2
             in all checkBound bounds
+    Choice{}   == _ = False
     Notify obs1 == Notify obs2 = obs1 == obs2
-    _ == _ = False
+    Notify{} == _ = False

 instance Eq a => Eq (Case a) where
     {-# INLINABLE (==) #-}
     Case acl cl == Case acr cr                       = acl == acr && cl == cr
+    Case{}      == _                                 = False
     MerkleizedCase acl bsl == MerkleizedCase acr bsr = acl == acr && bsl == bsr
-    _ == _                                           = False
+    MerkleizedCase{}       == _                      = False
